---
title: "Crowding and Development_Jan2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

During the summer of 2017, Melanie Smith, Matt Pahl, Gray Wilson, and Molly Albecker conducted an experiment in which we raised different densities (2, 4, or 8) of coastal and inland Hyla cinerea tadpoles in either freshwater or 4ppt salinity water. In doing so, we asked a) how does saltwater affect development and survival of coastal vs. inland tadpoles? b) how does competition affect development and survival of coastal and inland tadpoles? and c) how does saltwater exposure and competition interact to affect development and survival of coastal and inland tadpoles? 

I will analyze the growth and development data by investigating:  
1) how growth rates vary according to treatment
2) how survival varies according to treatment
3) how time to metamorphosis varies according to treatment
4) how size at metamorphosis (length and mass) vary according to treatment

Step one, load dependencies and data. 
```{r, include=FALSE}
# Code Dependencies
library(readr)
library(tidyr)
library(ggplot2)
library(plyr)
library(RColorBrewer)
library(reshape2)
library(bbmle)
library(survival)
library(blme)
library(nlme)
library(optimx)
library(dplyr)
library(merTools)
library(MASS)
library(reshape2)
library(brglm)
library(survminer)
library(lme4)
library(grid)
library(data.table)
```

```{r}
#Tadpole growth rate data
growth = read.csv("~/Desktop/Work/DataSets/Density2017/Density_Data.csv")
#growth = na.omit(growth)
#Tadpole survivorship, time to metamorphosis across development
meta = read.csv("~/Desktop/Work/DataSets/Density2017/Metadat.csv")

#ReLabel Density
meta$denlab = 0
for(i in 1:nrow(meta)){ 
  if (meta$Density[i] == "2"){meta$denlab[i] = "Low"}
  else if (meta$Density[i] == "4"){meta$denlab[i] = "Med"}
  else {meta$denlab[i] = "High"}
}

dodge <- position_dodge(width=0.5) 

```
** Growth Rates through Time **

To analyze growth through time according to density, location, and salinity, I will use the Gompertz growth formula.
```{r message=FALSE, warning=FALSE}
#Gompertz
Gom=function(x,initial,gamma,alpha){
  initial*exp(gamma/alpha*(1-exp(-alpha*x)))
}

#Gompertz
Wt=function(x,initial,Gamma,alpha){
  initial*exp(Gamma/alpha*(1-exp(-alpha*x)))
}
```

```{r}
#Create data frame

growth$locdensalwkrp <- paste(growth$Location,growth$Density,growth$Sal,growth$Week,growth$Replicate,sep = "_")


x = data.frame()
for(i in 1:length(unique(growth$locdensalwkrp))){
  xt = unique(growth$locdensalwkrp)[i]
  dat2 = filter(growth, locdensalwkrp == xt)
  length_mean = mean(dat2$Total.Length)
  x. = data.frame("Location" = unique(dat2$Location),
                  "Replicate" = unique(dat2$Replicate),
                  "Density" = unique(dat2$Density),
                  "Sal" = unique(dat2$Sal),
                  "Week" = unique(dat2$Week),
                  "Total.Length" = length_mean)
  x = rbind(x,x.)
  }

#x=data.frame(Total.Length=x$Total.Length,Week=x$Week,Location= x$Location,Sal= x$Sal,Density=x$Density)
#x=na.omit(x)
x$Sal.=as.factor(x$Sal)
x$Density. = as.factor(x$Density)
which(is.na(x$Total.Length))
```

```{r}
#Establish reasonable starting parameters
m=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=10,gamma=0.2,alpha=.1,stdv=5),  
        parameters=list(initial~1,gamma~1,alpha~1),
        method = "bobyqa", skip.hessian=FALSE)
summary(m)

nm1=unname(coef(m)) #extract starting coefficients
```

```{r}
# Candidate Models

m1=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~Density.,gamma~Location*Sal.*Density.,alpha~Location*Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m2=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.*Density.,alpha~Location+Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m3=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.*Density.,alpha~Location*Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

m4=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.*Density.,alpha~Location+Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

##

m5=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.*Density.,alpha~Location*Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m6=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.*Density.,alpha~Location+Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m7=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.*Density.,alpha~Location*Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

m8=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.*Density.,alpha~Location+Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

##

m9=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.+Density.,alpha~Location*Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m10=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.+Density.,alpha~Location+Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m11=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.+Density.,alpha~Location*Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

m12=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location*Sal.+Density.,alpha~Location+Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

##

m13=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.+Density.,alpha~Location*Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m14=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.+Density.,alpha~Location+Sal.*Density.),
        method = "bobyqa", skip.hessian=FALSE)

m15=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.+Density.,alpha~Location*Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

m16=mle2(Total.Length ~ dnorm(Gom(Week,initial,gamma,alpha),sd=stdv),
        data = x,
        optimizer = "optimx",
        start = list(initial=nm1[1],gamma=nm1[2],alpha=nm1[3],stdv=nm1[4]),  
        parameters=list(initial~1,gamma~Location+Sal.+Density.,alpha~Location+Sal.+Density.),
        method = "bobyqa", skip.hessian=FALSE)

#Use AIC to determine which is best fit model 
ICtab(m,m1,m2,m3,m4,m5,m6,m7,m8,
      m9,m10,m11,m12,m13,m14,m15,m16,weights=TRUE)

#Model 14 is the best fit
summary(m14) 
predict(m14)

#Diagnostics
x$resid = residuals(m14)[,1]
x$cup = growth$cup
ggplot(x,aes(x=Week,y=resid))+geom_jitter()+geom_smooth(method = lm,se=FALSE)
mod_diag = lm(resid~Week*cup, data = x)
mod_diag. = lm(resid~Week, data = x)
mod_diag.. = lm(resid~Week+cup, data = x)
mod_diag... = lm(resid~1, data = x)
ICtab(mod_diag...,mod_diag..,mod_diag.,mod_diag)
anova(mod_diag,mod_diag.)

#To extract coefficients for plotting
#View(coef(m14))
#View(confint(m14,method="quad"))
```
Plot results
```{r}
require(RColorBrewer)
require(plotly)
growth$sallocden = paste(growth$Sal,growth$Location,growth$Density,sep="_")
growth$salloc = paste(growth$Sal, growth$Location)
growth$Density = as.factor(growth$Density)
# Plotting colors
cols_up <- c("Inland" = "darkseagreen4", "Coastal" = "dodgerblue4")
cols_low <- c("inland" = "darkseagreen4", "coastal" = "dodgerblue4")
cols_locsal <- c("coastal_0"="dodgerblue4", "coastal_4"="blue", "inland_0"="darkseagreen4","inland_4"="green")
cols_salloc <- c("0_Coastal"="dodgerblue4", "4_Coastal"="blue", "0_Inland"="darkseagreen4","4_Inland"="green")
cols_sallocden <- c("0_Coastal_8" = "#66CCEE", "0_Coastal_4" = "#99EE88", "0_Coastal_2" = "#CC8899", "0_Inland_2" = "#CC0077",
                    "0_Inland_8" = "#CC2277",  "0_Inland_4" = "#009944",  "4_Inland_4" = "#f2d07f", "4_Coastal_4" = "#f2a717",
                    "4_Coastal_2" = "#CCAAFF", "4_Inland_2" = "#663388", "4_Inland_8" = "#FFFF77",  "4_Coastal_8" = "#664400")
line <- c("2" = "solid", "4" = "F1", "8" = "dashed")
line2 <- c("0"= "solid", "4" = "dashed")
# Labels for Facet Wrapping 
fac_label = c("2"="2 Tadpoles",
              "4"="4 Tadpoles",
              "8"="8 Tadpoles")
fac_label1 = c("0"="Freshwater (0.5ppt)",
              "4"="Saltwater (4ppt)")

modfit = data.frame(x,modpred = predict(m14))
modfit$sallocden = paste(modfit$Sal,modfit$Location,modfit$Density,sep="_")


d2d = ggplot(modfit, aes(x=Week ,y=Total.Length, group = sallocden, fill = Location, colour = Location))  + 
  geom_jitter(aes(x=Week,y=Total.Length),size=0.5,alpha = 1)+#xlim(0,35)+
  stat_smooth(aes(linetype = Density.),size = 2,se = TRUE,span = 3.5)+xlim(0,12.5)+
  scale_linetype_manual(values = line) +
  ylab("Total Length (mm)")+ xlab("Week")+
  scale_colour_manual(values = cols_up)+ 
  scale_fill_manual(values = cols_up)+
  theme_bw(base_size = 24, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")+
  facet_wrap(~Sal,labeller=labeller(Sal = fac_label1),nrow = 1)
  #facet_wrap(~salloc, labeller=labeller(Density = fac_label),nrow = 1)  
d2d


```

```{r}
#load a dataset with each coefficient (This needs to be updated)
dencoef = read.csv("~/Desktop/Work/DataSets/Density2017/Density_growth_coef.csv")
dencoef1 = dencoef[c(1:12),-c(1:5)] # Get the data in line


#ReLabel Density
dencoef1$denlab = 0
for(i in 1:nrow(dencoef1)){ 
  if (dencoef1$density[i] == "2"){dencoef1$denlab[i] = "Low"}
  else if (dencoef1$density[i] == "4"){dencoef1$denlab[i] = "Med"}
  else {dencoef1$denlab[i] = "High"}
}

dencoef1$salinity = as.factor(dencoef1$salinity)
dencoef1$trt = paste(dencoef1$location,dencoef1$salinity,dencoef1$density,sep="_")
dencoef1$locsal = paste(dencoef1$location,dencoef1$salinity,sep="_")
```

```{r}
# Plot Alpha
alphaden = ggplot(data=dencoef1, aes(x = reorder(denlab,density), y = alpha, group = locsal, shape=location, colour=location)) + 
  ylab("Exponential Decay of Growth")+ xlab("Tadpole Density")+
  scale_colour_manual(values = cols_low)+ #xlim(-0.5,6.5)+
  scale_fill_manual(values = cols_low)+
  scale_shape_manual(values = c("inland" = 17, "coastal" = 16))+
  theme_bw(base_size = 24, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
alphaden1 = alphaden + #stat_smooth(method="glm") +
  geom_line(aes(colour=location),linetype = 2,width = 0.25,position_dodge = 0.2)+
  geom_point(aes(colour=location),size=8,position_dodge = 0.2)+
  geom_errorbar(aes(ymin=alpha_lwr,ymax=alpha_upr,colour=location),width=0.2,position_dodge = 0.2)+
  facet_wrap(~salinity,labeller=labeller(salinity = fac_label1),nrow = 1)
alphaden1

```

```{r}
# Plot Gamma
gammaden = ggplot(data=dencoef1, aes(x =reorder(denlab,density), y = gamma, group = locsal, shape = location,colour=location)) + 
  ylab("Size Specific Growth Rate")+ xlab("Tadpole Density")+
  scale_colour_manual(values = cols_low)+ #xlim(-0.5,6.5)+
  scale_fill_manual(values = cols_low)+
  scale_shape_manual(values = c("inland" = 17, "coastal" = 16))+
  theme_bw(base_size = 24, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
gammaden1 = gammaden + #stat_smooth(method="glm") 
  geom_line(aes(colour=location),linetype = 2)+
  geom_errorbar(aes(ymin=gamma_lwr,ymax=gamma_upr,colour=location),width=0.2)+
  geom_point(aes(colour=location),size=8)+
  facet_wrap(~salinity,labeller=labeller(salinity = fac_label1),nrow = 1)
gammaden1

```

Tadpole mortality

```{r}
detach(package:plyr) 

denmort1 = meta %>% #To calculate the proportion individuals that survived to metamorphosis
  group_by(Location,Sal,denlab,Replicate) %>%
  summarise(ct = length(Dead),
            cat = sum(Dead),
            prop.surv = (cat/ct)) 

denmort1$Sal. = as.factor(denmort1$Sal)
denmort1$denlab. = as.factor(denmort1$denlab)
denmort1$salloc = paste(denmort1$Sal,denmort1$Location,sep="_") #for plotting later

```

```{r}

#convergence was tricky for this test
#source(system.file("utils", "allFit.R", package="lme4"))
#a1.all <- allFit(a1) #Tests which convergence methods will work and which won't. Bobyqa works.

a1 = bglmer(prop.surv ~ Sal + denlab. + Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))
a2 = bglmer(prop.surv ~ Sal. * denlab. * Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
           glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))
a3 = bglmer(prop.surv ~ Sal. + denlab. * Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))
a4 = bglmer(prop.surv ~ Sal. * denlab. + Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))

anova(a1,a2)
anova(a1,a3)
anova(a1,a4) #additive model is best

summary(a1)
```

```{r}
a5 = bglmer(prop.surv ~ 1 + denlab. + Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))
a6 = bglmer(prop.surv ~ Sal. + 1 + Location + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))
a7 = bglmer(prop.surv ~ Sal. + denlab. + 1 + (1|Replicate), 
            data = denmort1, family = binomial(), weights = ct,
            glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=20000)))

anova(a1,a5) # no salinity effect (p = 0.58)
anova(a1,a6) # effect of density (p = 0.0006)
anova(a1,a7) # no location effect (p = 0.29)

```

```{r}
#Full Plot 
survplot <- expand.grid(Sal = unique(denmort1$Sal),
                      #denlab. = seq(0,8, length = 50),
                      denlab. = unique(denmort1$denlab.),
                      Location = unique(denmort1$Location),
                      prop.surv=0)
mm = model.matrix(terms(a1),survplot)
survplot$prop.surv = mm %*% fixef(a1)
pvar1 <- diag(mm %*% tcrossprod(vcov(a1),mm))
#tvar1 <- pvar1+VarCorr(b4b)$plot[1]
survplot <- data.frame(
  survplot
  , plo = survplot$prop.surv-1.96*sqrt(pvar1)
  , phi = survplot$prop.surv+1.96*sqrt(pvar1)
  #, tlo = propsurvplot$binary_hatch-2*sqrt(tvar1)
  #, thi = propsurvplot$binary_hatch+2*sqrt(tvar1)
)
survplot=data.frame(survplot[,1:3],apply(survplot[,4:6],2,plogis))
survplot$trt = paste(survplot$Sal,survplot$denlab.,survplot$Location,sep="_")
survplot$salloc = paste(survplot$Sal,survplot$Location,sep="_")

shipshape <- c("0" = 16, "4" = 17)

o1 = ggplot(data=survplot,aes(x=denlab.,y=prop.surv,group=salloc))+
  xlab("Tadpole Density")+
  ylab("Survivorship at Metamorphosis")+ ylim(0.25,1)+
  #geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  #geom_line(aes(group=salloc, color=Location, linetype = factor(Sal)), size = 2)+
  scale_linetype_manual(values = line2) +
  scale_x_discrete(limits=c("Low","Med","High"))+
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  theme(legend.position="none")+theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
o2 = o1 + 
  geom_line(aes(colour=Location),position = dodge, linetype = 2)+
  geom_errorbar(aes(ymin=plo,ymax=phi,colour=Location), position= dodge,width=0.3)+
  geom_point(aes(colour=Location,shape = factor(Sal)), position = dodge, size=8)+
 #geom_jitter(data = denmort1, aes(x = factor(Density), y = prop.surv, 
                                    #       group = salloc, colour = Location, shape = factor(Sal)), size = 2) +
  scale_shape_manual(values = shipshape)
o2
```

```{r}
#plot raw summary data
denmort2 = denmort1 %>% #To calculate the proportion individuals that survived to metamorphosis
  group_by(Location,Sal,denlab.) %>%
  summarise(surv = mean(prop.surv),
            surverr = sd(prop.surv),
            n = length(prop.surv)) 
denmort2$se = denmort2$surverr/(sqrt(denmort2$n))
denmort2$salloc = paste(denmort2$Sal,denmort2$Location,sep="_")
denmort2$phi = denmort2$surv + (denmort2$se)
denmort2$plo = denmort2$surv - (denmort2$se)

shipshape2 = c("0_Coastal"=16, "4_Coastal"=1, "0_Inland"=17,  "4_Inland"=2)
o1 = ggplot(data=denmort2,aes(x=denlab.,y=surv,group=salloc,colour = Location))+
  xlab("Tadpole Density")+
  ylab("Survivorship at Metamorphosis")+ #ylim(0.4,1)+
  #geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  #geom_line(aes(group=salloc, color=Location, linetype = factor(Sal)), size = 2)+
  scale_linetype_manual(values = line2) +
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  scale_x_discrete(limits=c("Low","Med","High"))+
  theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
o2 = o1 + 
  #geom_line(aes(colour=Location),position = dodge, linetype = 2)+
  geom_errorbar(aes(ymin=plo,ymax=phi,colour=Location), position= dodge,width=0.3)+
  geom_point(aes(colour=Location,shape = factor(salloc)), position = dodge, size=8)+
 #geom_jitter(data = denmort1, aes(x = factor(Density), y = prop.surv, 
                                    #       group = salloc, colour = Location, shape = factor(Sal)), size = 2) +
  scale_shape_manual(values = shipshape2)
o2
```
Time to Metamorphosis
```{r}
#Dataset filtered for just for those that made it to metamorphosis
metamm= filter(meta,Dead != "0")
metamm$salloc = paste(metamm$Sal,metamm$Location,sep="_") #for plotting later

#For those that made it to metamorphosis, are there differences in timing according to treatment/location? 
b1 = glmer(Time_MM ~ Location * denlab * Sal+ (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa"))
b2 = glmer(Time_MM ~ Location * denlab + Sal + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa"))
b3 = glmer(Time_MM ~ Location + denlab * Sal + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa")) 
b4 = glmer(Time_MM ~ Location + denlab +Sal + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa"))

anova(b1,b4) #No interaction
anova(b4,b2)
anova(b4,b3) #There is interaction between Density and Salinity
```

```{r}
#Likelihood Ratio Testing
b5 = glmer(Time_MM ~ 1 + denlab + Sal + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa")) 
b6 = glmer(Time_MM ~ Location + 1 + Sal + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa")) 
b7 = glmer(Time_MM ~ Location + denlab + 1 + (1|Replicate), data = metamm, 
            family = poisson(),control=glmerControl(optimizer = "bobyqa")) 

anova(b4,b5) # Location is not significant (p = 0.39)
anova(b4,b6) # Density is significant (p < 0.0001)
anova(b4,b7) # Salinity is significant (p = 0.03)

```

```{r}
#Full Plot 
timeplot <- expand.grid(Sal = unique(metamm$Sal),
                      #Density = seq(0,8, length = 50),
                      Density = unique(denmort1$Density),
                      Location = unique(metamm$Location),
                      Time_MM=0)
mm = model.matrix(terms(b3),timeplot)
timeplot$Time_MM = mm %*% fixef(b3)
pvar1 <- diag(mm %*% tcrossprod(vcov(b3),mm))
#tvar1 <- pvar1+VarCorr(b4b)$plot[1]
timeplot <- data.frame(
  timeplot
  , plo = timeplot$Time_MM-1.96*sqrt(pvar1)
  , phi = timeplot$Time_MM+1.96*sqrt(pvar1)
  #, tlo = propsurvplot$binary_hatch-2*sqrt(tvar1)
  #, thi = propsurvplot$binary_hatch+2*sqrt(tvar1)
)
timeplot=data.frame(timeplot[,1:3],apply(timeplot[,4:6],2,exp))
timeplot$trt = paste(timeplot$Sal,timeplot$Density,timeplot$Location,sep="_")
timeplot$salloc = paste(timeplot$Sal,timeplot$Location,sep="_")

b8 = ggplot(data=timeplot,aes(x=Density,y=Time_MM,group=salloc))+
  xlab("Density of Tadpole Environment")+
  ylab("Time to Metamorphosis (days)")+
  geom_line(aes(colour=Location),position = dodge, linetype = 2)+
  geom_errorbar(aes(ymin=plo,ymax=phi,colour=Location), position= dodge,width=0.3)+
  geom_point(aes(colour=Location,shape = factor(Sal)), position = dodge, size=8)+
 #geom_jitter(data = denmort1, aes(x = factor(Density), y = prop.surv, 
                                    #       group = salloc, colour = Location, shape = factor(Sal)), size = 2) +
  #geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  #geom_point(data = metamm, aes(x = Density, y = Time_MM, group = salloc, colour = Location, shape = factor(Sal)), position = dodge,size = 2)+
  scale_shape_manual(values = shipshape)+
  #geom_line(aes(group=salloc, color=Location,linetype = factor(Sal)),size =2)+
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  scale_linetype_manual(values = line2) +
  theme(legend.position="none")+theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none") + xlim(1,8.2)
b8
```
```{r}
#Raw Data Plots
matamm1  = metamm %>% #To calculate the proportion individuals that survived to metamorphosis
  group_by(Location,Sal,denlab) %>%
  summarise(surv = mean(Time_MM,na.rm=TRUE),
            surverr = sd(Time_MM,na.rm=TRUE),
            n = length(Time_MM)) 
matamm1$se = matamm1$surverr/(sqrt(matamm1$n))
matamm1$salloc = paste(matamm1$Sal,matamm1$Location,sep="_")
matamm1$phi = matamm1$surv + (matamm1$se)
matamm1$plo = matamm1$surv - (matamm1$se)

b8 = ggplot(data=matamm1,aes(x=denlab,y=surv,group=salloc,colour = Location))+
  xlab("Tadpole Density")+
  ylab("Time to Metamorphosis (days)")+ #ylim(0.4,1)+
  #geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  #geom_line(aes(group=salloc, color=Location, linetype = factor(Sal)), size = 2)+
  scale_linetype_manual(values = line2) +
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  scale_x_discrete(limits=c("Low","Med","High"))+
  theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
b9 = b8 + 
  #geom_line(aes(colour=Location),position = dodge, linetype = 2)+
  geom_errorbar(aes(ymin=plo,ymax=phi,colour=Location), position= dodge,width=0.35)+
  geom_point(aes(colour=Location,shape = salloc), position = dodge, size=8)+
 #geom_jitter(data = denmort1, aes(x = factor(Density), y = prop.surv, 
                                    #       group = salloc, colour = Location, shape = factor(Sal)), size = 2) +
  scale_shape_manual(values = shipshape2)
b9
```

Mass at Metamorphosis
```{r}

# Are there differences in weight at metamorphosis due to location or trt?
c1 = lmer(log(Final_mass) ~ Sal * Density * Location + (1|Replicate), data = metamm)
c2 = lmer(log(Final_mass) ~ Sal + Density + Location + (1|Replicate), data = metamm)
c3 = lmer(log(Final_mass) ~ Sal * Density + Location + (1|Replicate), data = metamm)
c4 = lmer(log(Final_mass) ~ Sal + Density * Location + (1|Replicate), data = metamm)

anova(c1,c2)
anova(c2,c3)
anova(c2,c4) #additive model (c2) is best

#Likelihood ratio testing
c5 = lmer(log(Final_mass) ~ 1 + Density + Location + (1|Replicate), data = metamm)
c6 = lmer(log(Final_mass) ~ Sal + 1 + Location + (1|Replicate), data = metamm)
c7 = lmer(log(Final_mass) ~ Sal + Density + 1 + (1|Replicate), data = metamm)

anova(c2,c5) # Salinity not significant (p = 0.71)
anova(c2,c6) # Density is significant (p = 0.03)
anova(c2,c7) # Location is not significant (p = 0.27)

```

```{r}
#Full Plot 
massplot <- expand.grid(Sal = unique(metamm$Sal),
                      Density = seq(0,8, length = 50),
                      #Density = unique(denmort1$Density),
                      Location = unique(metamm$Location),
                      Final_mass=0)
mm = model.matrix(terms(c2),massplot)
massplot$Final_mass = mm %*% fixef(c2)
pvar1 <- diag(mm %*% tcrossprod(vcov(c2),mm))
#tvar1 <- pvar1+VarCorr(b4b)$plot[1]
massplot <- data.frame(
  massplot
  , plo = massplot$Final_mass-1.96*sqrt(pvar1)
  , phi = massplot$Final_mass+1.96*sqrt(pvar1)
  #, tlo = propsurvplot$binary_hatch-2*sqrt(tvar1)
  #, thi = propsurvplot$binary_hatch+2*sqrt(tvar1)
)
massplot=data.frame(massplot[,1:3],apply(massplot[,4:6],2,exp))
massplot$trt = paste(massplot$Sal,massplot$Density,massplot$Location,sep="_")
massplot$salloc = paste(massplot$Sal,massplot$Location,sep="_")

c8 = ggplot(data=massplot,aes(x=Density,y=Final_mass,group=salloc))+
  xlab("Density of Tadpole Environment")+
  ylab("Mass at Metamorphosis (g)")+
  geom_line(aes(group=salloc, color=salloc),size =2)+
  geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=salloc),alpha=.2)+
  scale_colour_manual(values = cols_salloc) +
  scale_fill_manual(values = cols_salloc) +
  theme(legend.position="none")+theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))
c9 = c8 + geom_jitter(data = metamm, aes(x = Density, y = Final_mass, group = salloc, colour = salloc), size = 2)
c9
```
Length at Metamorphosis
```{r}

# Are there differences in weight at metamorphosis due to location or trt?
d1 = lmer(log(MM_total) ~ Sal * Density * Location + (1|Replicate), data = metamm)
d2 = lmer(log(MM_total) ~ Sal + Density + Location + (1|Replicate), data = metamm)
d3 = lmer(log(MM_total) ~ Sal * Density + Location + (1|Replicate), data = metamm)
d4 = lmer(log(MM_total) ~ Sal + Density * Location + (1|Replicate), data = metamm)

anova(d1,d2)
anova(d2,d3)
anova(d2,d4) #additive model (d2) is best

#Likelihood ratio testing
d5 = lmer(log(MM_total) ~ 1 + Density + Location + (1|Replicate), data = metamm)
d6 = lmer(log(MM_total) ~ Sal + 1 + Location + (1|Replicate), data = metamm)
d7 = lmer(log(MM_total) ~ Sal + Density + 1 + (1|Replicate), data = metamm)

anova(d2,d5) # Salinity not significant (p = 0.74)
anova(d2,d6) # Density is nearly significant (p = 0.06)
anova(d2,d7) # Location is significant (p = 0.003)

```

```{r}
#Full Plot 
lenplot <- expand.grid(Sal = unique(metamm$Sal),
                      #Density = seq(0,8, length = 50),
                      Density = unique(metamm$Density),
                      Location = unique(metamm$Location),
                      MM_total=0)
mm = model.matrix(terms(d2),lenplot)
lenplot$MM_total = mm %*% fixef(d2)
pvar1 <- diag(mm %*% tcrossprod(vcov(d2),mm))
#tvar1 <- pvar1+VarCorr(b4b)$plot[1]
lenplot <- data.frame(
  lenplot
  , plo = lenplot$MM_total-1.96*sqrt(pvar1)
  , phi = lenplot$MM_total+1.96*sqrt(pvar1)
  #, tlo = propsurvplot$binary_hatch-2*sqrt(tvar1)
  #, thi = propsurvplot$binary_hatch+2*sqrt(tvar1)
)
lenplot=data.frame(lenplot[,1:3],apply(lenplot[,4:6],2,exp))
lenplot$trt = paste(lenplot$Sal,lenplot$Density,lenplot$Location,sep="_")
lenplot$salloc = paste(lenplot$Sal,lenplot$Location,sep="_")

d8 = ggplot(data=lenplot,aes(x=Density,y=MM_total,group=salloc))+
  xlab("Tadpole Density")+
  ylab("Length at Metamorphosis (mm)")+
  geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  geom_point(data = metamm, aes(x = Density, y = MM_total, group = salloc, 
                                colour = Location,shape=factor(Sal)),position=dodge, size = 2)+
  geom_line(aes(group=salloc, color=Location,linetype=factor(Sal)),size =2)+
  scale_shape_manual(values = shipshape)+
  scale_linetype_manual(values = line2) +
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica") + 
  theme(strip.background =element_rect(fill="white")) +
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
d8

```
```{r}
#Raw Data Plots
matamm1  = metamm %>% #To calculate the proportion individuals that survived to metamorphosis
  group_by(Location,Sal,denlab) %>%
  summarise(surv = mean(MM_total,na.rm=TRUE),
            surverr = sd(MM_total,na.rm=TRUE),
            n = length(MM_total)) 
matamm1$se = matamm1$surverr/(sqrt(matamm1$n))
matamm1$salloc = paste(matamm1$Sal,matamm1$Location,sep="_")
matamm1$phi = matamm1$surv + (matamm1$se)
matamm1$plo = matamm1$surv - (matamm1$se)

c8 = ggplot(data=matamm1,aes(x=denlab,y=surv,group=salloc))+
  xlab("Tadpole Density")+
  ylab("Length at Metamorphosis (mm)")+ #ylim(0.4,1)+
  #geom_ribbon(aes(ymin = plo, ymax = phi, group=salloc,fill=Location),alpha=.2)+
  #geom_line(aes(group=salloc, color=Location, linetype = factor(Sal)), size = 2)+
  scale_linetype_manual(values = line2) +
  scale_colour_manual(values = cols_up) +
  scale_fill_manual(values = cols_up) +
  scale_x_discrete(limits=c("Low","Med","High"))+
  theme_bw()+
  #scale_y_continuous(limits = c(0, 1))+
  #geom_jitter(data=tadmort4,aes(x = tad,y = prop.alive,group=eggloc,color=eggloc))+
  theme_bw(base_size = 30, base_family = "Helvetica")+ 
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  theme(axis.ticks = element_line(colour = "black"))+
  theme(axis.text= element_text(colour = "black"))+
  theme(legend.position="none")
c9 = c8 + 
  #geom_line(aes(colour=Location),position = dodge, linetype = 2)+
  geom_errorbar(aes(ymin=plo,ymax=phi,colour=Location), position= dodge,width=0.35)+
  geom_point(aes(colour=Location,shape = salloc), position = dodge, size=8)+
 #geom_jitter(data = denmort1, aes(x = factor(Density), y = prop.surv, 
                                    #       group = salloc, colour = Location, shape = factor(Sal)), size = 2) +
  scale_shape_manual(values = shipshape2)
c9
```